### 2020-02-11 submission/nlp_models.tex
all updates

    \subfigure[PL exponent ($\alpha$)]{
        \includegraphics[width=4.0cm]{img/GPT2*_fnl_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    \subfigure[Log Alpha Norm]{
        \includegraphics[width=4.0cm]{img/GPT2*_fnl_logpnorm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{Histogram of PL exponents ($\alpha$)
             %Log Spectral norm ($\log\Vert\mathbf{W}\Vert_{\infty}$), 
              and Log Alpha Norm ($\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$) for weight matrices from models of different sizes in the GPT2 architecture series.  (Plots omit the first 2 (embedding) layers, because they are normalized differently giving anamolously large values.)
              \michael{CAN WE HAVE OTHER FIGS, THEY WERE MORE VISUALLY COMPELLING.}
             }
    \label{fig:gpt2-histograms}
\end{figure}

>>>>

    \subfigure[PL exponent ($\alpha$)]{
        \includegraphics[width=4.0cm]{img/GPT2*_fnl_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    \subfigure[Log Alpha Norm]{
        \includegraphics[width=4.0cm]{img/GPT2*_fnl_logpnorm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{Histogram of PL exponents ($\alpha$)
             %Log Spectral norm ($\log\Vert\mathbf{W}\Vert_{\infty}$), 
              and Log Alpha Norm ($\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$) for weight matrices from models of different sizes in the GPT2 architecture series.  (Plots omit the first 2 (embedding) layers, because they are normalized differently giving anamolously large values.)
             }
    \label{fig:gpt2-histograms}
\end{figure}
